Sparse associative memories

### 2014-06-22 Articles/article.tex
...

	For one iteration, winner takes all is the same as winners take all.

	Winners take all better with errors instead of erasures.

>>>>

	For one iteration, winner takes all is the same as $a$-winners take all.

	For multiple iterations $a$-winner take all is an improvement.

	"$a$-Winners take all" better than "winner takes all" with errors instead of erasures.
